### 2017-12-13 Paper/main.tex
Updates from ShareLaTeX

% \Mark is probably provided by spconf, that I don't have
\newcommand{\Mark}[1]{\textsuperscript{#1}}

@@

After the model setting we set a series of condition that create the signal. Such condition are highlighted in the following diagram.

\section{Evidence and findings}
After 930 rounds, that is we run the sequence for all the stocks in the portfolio, we got the following conclusion:
\begin{itemize}
    \item the model out perform the naive algorithm;
    \item the model failed to predict in a consistent way whether the price was going up or down;
    \item either the models alone failed to do so;
    \item the plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}

>>>>

\newcommand{\Mark}[1]{\textsuperscript{#1}}

@@

After the model setting we set a series of condition that create the signal. Such condition are highlighted in the following flowchart.

\begin{tikzpicture}

\end{tikzpicture}

\section{Evidence and findings}
After 930 rounds, that is we run the sequence for all the stocks in the portfolio, we got the following conclusion:
\begin{itemize}
    \item The model out perform the naive algorithm;
    \item The model failed to predict in a consistent way whether the price was going up or down;
    \item Either the models alone failed to do so;
    \item The plain ARIMA performed purely in comparison with the hybrid model.
\end{itemize}
